Dynamic Topic Modeling for Voice Dialogues

### 2024-05-16 paper/main.tex
update experimetns

\begin{lstlisting}
    <|user|> 
    <dialogue> 
    Please list of high-level topic words 
    in the following dialogue:
    <|assistant|>
\end{lstlisting}

The appearance of the keywords <|user|>, <|assistant|> dependes on type of LLM.

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            \hline
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

\textbf{Baseline Models}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Product} &  \multicolumn{3}{| c |}{Academic} & \multicolumn{3}{| c |}{Committee} \\
        \hline
        model  & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        whisper-large +  &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \hline
        model &  Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Product} &  \multicolumn{3}{| c |}{Academic} & \multicolumn{3}{| c |}{Committee} \\
        \hline
        model  & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TC & TD & TC & TD \\ 
        \hline
        LLaMA3 8B & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d \\ 
        Mistral 7B & c & d & c & d \\ 
        \hline
        BertTopic & c & d & c & d \\
        LSA  & c & d & c & d \\
        \hline
    \end{tabular}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Product} &  \multicolumn{2}{| c |}{Academic} & \multicolumn{2}{| c |}{Committee} \\
        \hline
        model  & TC & TD & TC & TD & TC & TD  \\ 
        \hline
        LLaMA3 8B & c & d & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d & c & d \\ 
        Mistral 7B & c & d & c & d & c & d \\ 
        \hline
        BertTopic & c & d & c & d & c & d \\ 
        LSA & c & d & c & d & c & d \\ 
        \hline
    \end{tabular}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Various approaches for topic diarization, dialogue segmentation, topic extraction, and topic evolution have been explored;
    \item The search for suitable text and audio datasets was conducted, and the selected datasets were analysed and preprocessed for experiments at all stages and for the entire pipeline.
    \item In the context of the dialog segmentation stage, the optimal open-source solution was identified and the BERT model was subjected to detailed analysis.  This approach has been prepared and integrated into the general pipeline.
    \item At the topic extraction stage, new approaches utilising generative models were investigated. Furthermore, a range of large language models, including LlaMA and Mistral, were examined, along with novel features that enhance the default architecture of the Transformer.
    \item Topic Evolution
    \item A suitable set of metrics was identified and selected to evaluate the quality of each stage. In order to utilise the metrics, a library with an implementation was Investigated and integrated into pipeline.
\end{itemize}

>>>>

\begin{lstlisting}
    <|user|> 
    <dialogue> 
    Give me N topic words 
    from the following dialogue:
    <|assistant|>
\end{lstlisting}

where N is number of topic words, the appearance of the keywords <|user|>, <|assistant|> dependes on type of LLM.

Moreover, in experiments, models are tested not only in zero-hour mode, but also in few-shot.
A few-short is a technique in which there are examples of a query with an answer before the main question.
In this case the prompt for LLM will look like this:

\begin{lstlisting}
    <|user|> 
    <example_dialogue1> 
    Give me N topic words 
    from the following dialogue:
    <example_answer1>

    <example_dialogue2> 
    Give me N topic words 
    from the following dialogue:
    <example_answer2>

    <dialogue> 
    Give me N topic words 
    from the following dialogue:
    <|assistant|>
\end{lstlisting}

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & - \\ 
            \hline
            Product Meetings (QMSum) & 137 & 535.6 & - \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & - \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & - \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{1}{| c |}{Product} &  \multicolumn{1}{| c |}{Academic} & \multicolumn{1}{| c |}{Committee} \\
        \hline
        model  & \multicolumn{3}{| c |}{DER} \\ 
        \hline
        whisper-large & der & der & der \\ 
        pyannote-diarisation &  der & der & der \\ 
        bert-large NSP & der & der & der \\ 
        \hline
    \end{tabular}
    \captionof{table}{Speaker diarization evaluation}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \hline
        model & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        TeT & 0.469 & 0.488 & 0.204 & 0.446 & 0.458 & 0.378 \\
        TeT + Embedding & 0.469 & 0.488 & 0.204 & 0.446 & 0.458 & 0.378 \\ 
        TeT + NSP & 0.425 & 0.439 & 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline
        bert-base NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Text datasets segmentation}
\end{center}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Product} &  \multicolumn{3}{| c |}{Academic} & \multicolumn{3}{| c |}{Committee} \\
        \hline
        model  & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        TeT & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        TeT + Embedding & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        TeT + NSP &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\  
        \hline
        bert-base NSP &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Audio datasets segmentation}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TC & TD & TC & TD \\ 
        \hline
        BertTopic & c & d & c & d \\
        LSA  & c & d & c & d \\
        \hline
        LLaMA3 8B & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d \\ 
        Mistral 7B & c & d & c & d \\ 
        \hline
    \end{tabular}
    \captionof{table}{Text datasets topics extraction}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Product} &  \multicolumn{2}{| c |}{Academic} & \multicolumn{2}{| c |}{Committee} \\
        \hline
        model  & TC & TD & TC & TD & TC & TD  \\ 
        \hline
        BertTopic & c & d & c & d & c & d \\ 
        LSA & c & d & c & d & c & d \\ 
        \hline
        LLaMA3 8B & c & d & c & d & c & d \\ 
        Qwen1.5 7B & c & d & c & d & c & d \\ 
        Mistral 7B & c & d & c & d & c & d \\ 
        \hline
    \end{tabular}
    \captionof{table}{Audion datasets topics extraction}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Various approaches for topic diarization, dialogue segmentation, topic extraction, and topic evolution have been explored and the best of them were adopted to DTM pipeline;
    \item The search for suitable text and audio datasets was conducted, and the selected datasets were analysed and preprocessed for experiments at all stages and for the entire pipeline.
    \item In the context of the dialog segmentation stage, the optimal open-source solution was identified and the BERT model was subjected to detailed analysis.  This approach has been prepared and integrated into the general pipeline.
    \item At the topic extraction stage, new approaches utilising generative models were investigated. Furthermore, a range of large language models, including LlaMA and Mistral, were examined, along with novel features that enhance the default architecture of the Transformer.
    \item Topic Evolution
    \item A suitable set of metrics was identified and selected to evaluate the quality of each stage. In order to utilise the metrics, a library with an implementation was Investigated and integrated into pipeline.
\end{itemize}
